<span style='line-height:60px; font-size:60px'>Changing communicative need<br>predicts lexical competition<br>and contributes<br>to language change</span></font>

### 2019-08-19 ruse2019/index.Rmd
ruse talk

```{r, out.height=440, out.width="80%", dpi=500, eval=F}
#<font size="3pt">
library(magrittr)
library(plotly, quietly = T)
trendplot %>% layout(legend = list(orientation = 'h', font = list(size = 12)))
#plot(1)
```
<img src="img/trends.png" width="80%" />

@@

<img src="img/resultsplot.png" width="90%"/>

@@

```{r, fig.height=5, out.width="50%", eval=F}
displot
```
<img src="img/polysemy.png" width="40%"/>

>>>>

```{r, out.height=440, out.width="80%", dpi=500, eval=F}
#<font size="3pt">
library(magrittr)
library(plotly, quietly = T)
trendplot %>% layout(legend = list(orientation = 'h', font = list(size = 12)))
#plot(1)
```
<img src="img/trends.PNG" width="80%" />

@@

<img src="img/resultsplot.PNG" width="90%"/>

@@

```{r, fig.height=5, out.width="50%", eval=F}
displot
```
<img src="img/polysemy.PNG" width="40%"/>
